### 2022-07-21 manuscript_proof/manuscript.tex
Update on Overleaf.

% Overview of relevant methods and why we don't use them
It is well-known that GWAS can be sensitive to confounding variables. Shared ancestry among individuals, especially between close relatives, can give rise to spurious genetic correlations with a trait. Corrections for these types of population structure in human GWAS cohorts are well-developed and widely accepted  \citep{Astle2009, Price2006}. More recently, analogous methods have been developed for microbial GWAS, where clonal reproduction exacerbates population structure \citep{Power2017}. Microbial GWAS-specific phylogenetic methods to account for population structure in microbial GWAS include explicitly testing for lineage-specific effects as in \cite{Earle2016} and modified association tests that account for phylogenetic relationships amongst samples as in \cite{collins_phylogenetic_nodate}. These approaches are designed to quantify genetic effects from one organism on a trait.

>>>>

% Overview of relevant methods and why we don't use them
It is well-known that GWAS can be sensitive to confounding variables. Shared ancestry among individuals, especially between close relatives, can give rise to spurious genetic correlations with a trait. Corrections for these types of population structure in human GWAS cohorts are well-developed and widely accepted  \citep{Astle2009, Price2006}. More recently, analogous methods have been developed for microbial GWAS, where clonal reproduction exacerbates population structure \citep{Power2017}. Microbial GWAS-specific phylogenetic methods to account for population structure include explicitly testing for lineage-specific effects as in \cite{Earle2016} and modified association tests that account for phylogenetic relationships amongst samples as in \cite{collins_phylogenetic_nodate}. These approaches are designed to quantify genetic effects from one organism on a trait.
